Persistence of marine populations under climate and fishing

### 2015-02-19 Writing/final_draft/Appendix.tex
add axes and moved tick marks in figures and added all rockfish figures to appendix
updating Appendix to add figures
starting Malin's edits. Appendix is unfinished

\appendix
\section{Appendix}
In Appendix \ref{stab}, we provide the details for assessing the persistence of a population with an integrodifference model and we discuss the effect of the harvesting function on population persistence.  In Appendix \ref{sep}, we provide the details for assessing population persistence with separable dispersal kernels.  In Appendix \ref{gausapp} and \ref{sinapp}, we derive expressions for the critical harvesting rate and rate of environmental shift for Gaussian and sinuosoidal dispersal kernels.  In Appendix \ref{approxcrit}, we derive approximate expressions for these critical rates. In Appendix \ref{MPA} we provide details on differences between small and large MPA simulations. In Appendix \ref{rock} we parameterize our model for black rockfish in the California Current and demonstrate results for those parameters that are qualitatively similar to those presented in the main text.

@@

%\pagebreak
\subsection{California Current Black Rockfish Parameterization \label{rock}}
We parameterize our model for black rockfish in the California Current, with MPAs of spacing and width that is qualitatively similar to the MLP Act reserves, and with a maximum climate velocity equal to that observed empirically. The parameters and references are provided in Table \ref{rockfish_params}.

@@

\begin{table}[htdp]
\caption{\label{rockfish_params} Rockfish simulation parameters}
\begin{center}
\begin{tabular}{c l l}
\hline
Parameter & Value & Source\\
\hline
$R_0$ & 2.86 & \citet{white2010decision}, equivalent to $\left(\frac{1}{CRT}\right)$ \\
$K$ & 1 & \citet{white2010decision} \\
$h$ & 0-100\% &\\
$c$ & 0-200km/decade & \citet{burrows2011pace}\\
$L$ & 1000km & \\
MPA width & 20km & \citet{Gainesetal2010}\\
Space between MPAs & 76km & \citet{Gainesetal2010}\\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{plots/compare_flucts.png}
\caption{\label{fluctuations} Total population biomass is on the y axis, and generation is on the x axis. These simulations were run with climate velocity $ = 0.1$, and a proportional harvest rate $= 0.02$. }
% see bounded\_flux.R for code that made this plot
\end{figure}

\begin{figure}[h]
\centering
\caption{ \label{crith_rockfish}
 Lines indicate the critical threshold for persistence as a function of harvesting rate on the y-axis and climate velocity as a fraction of the length of the viable patch on the x-axis from an approximated Gaussian dispersal kernel as parameterized for black rockfish. }
 \end{figure}

 \begin{figure}[h]
 \centering
 \caption{ \label{synergy_rockfish}
 (a) The equilibrium biomass of the population as a function of the climate velocity relative to patch length on the x-axis and the proportional harvesting rate on the y-axis. (b) Interaction between the two stressors as a function of climate velocity and harvesting rate. The heat map indicates the interaction measure $S$, i.e., the loss in biomass in the doubly stressed population in excess of the sum of the losses caused by each stressor individually ($E_{hc}-E_h-E_c$). $S$ of $0$ indicates additive interaction of the stressors. The excess loss, on the order of $0.001$, is small in comparison to the total biomass, which can be as large as $20$. These results are from an approximated Gaussian dispersal kernel as parameterized for  black rockfish.
 }
 \end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{plots/rockfish_sims.pdf}
\caption{\label{simulation_rockfish} The equilibrium biomass of the population as a function of the climate velocity relative to patch length on the x-axis and the harvesting rate on the y-axis under alternative management strategies as parameterized for black rockfish. (a) The equilibrium biomass for simulations with constant harvest rates. (b) Equilibrium biomass for simulations with threshold management. For threshold management, the maximum threshold below which no harvesting is allowed is set to be the largest population size observed at a given time step before harvesting. For a less sever threshold, we use a proportion of this maximum threshold, so that a lower proportion gives a lower threshold and allows for more harvesting. We show this proportion on the y-axis. (c) Equilibrium biomass for simulations with protected areas where harvesting pressure outside reserves unchanged. (d) Equilibrium biomass for simulations with protected areas with harvesting pressure reallocated outside reserves.}
\end{figure}

\newpage
\bibliography{fish}

>>>>

\appendix
\section{Appendix}
In Appendix \ref{stab}, we provide the details for assessing the persistence of a population with an integrodifference model and we discuss the effect of the harvesting function on population persistence.  In Appendix \ref{sep}, we provide the details for assessing population persistence with separable dispersal kernels.  In Appendix \ref{gausapp} and \ref{sinapp}, we derive expressions for the critical harvesting rate and rate of environmental shift for Gaussian and sinuosoidal dispersal kernels.  In Appendix \ref{approxcrit}, we derive approximate expressions for these critical rates. In Appendix \ref{MPA} we provide details on differences between small and large MPA simulations. In Appendix \ref{rock} we parameterize our model for black rockfish in the California Current and demonstrate results for  parameters  which are qualitatively similar to those  presented in the main text.

@@

%\pagebreak
\subsection{California Current Black Rockfish Parameterization \label{rock}}
~\\We parameterize our model for black rockfish in the California Current, with MPAs of spacing and width that is qualitatively similar to the MLP Act reserves, and with a maximum climate velocity equal to that observed empirically. The parameters and references are provided in Table \ref{rockfish_params}.

@@

\begin{table}[htdp]
\caption{\label{rockfish_params} Rockfish simulation parameters}
\begin{center}
\begin{tabular}{c l l}
\hline
Parameter & Value & Source\\
\hline
$R_0$ & 2.86 & \citet{white2010decision}, equivalent to $\left(\frac{1}{CRT}\right)$ \\
$K$ & 1 & \citet{white2010decision} \\
$h$ & 0-100\% &\\
$c$ & 0-200km/decade & \citet{burrows2011pace}\\
$L$ & 1000km  & \citet{fishbase} \\
MPA width & 20km & \citet{Gainesetal2010}\\
Space between MPAs & 76km & \citet{Gainesetal2010}\\
Dispersal kernal &  Gaussian & \citet{white2010decision}\\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{../../plots/compare_flucts.png}
\caption{\label{fluctuations} Total population biomass is on the y axis, and generation is on the x axis. These simulations were run with climate velocity $ = 0.1$, and a proportional harvest rate $= 0.02$. }
% see bounded\_flux.R for code that made this plot
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{../../plots/rockfish_criticalh.pdf}
\caption{ \label{crith_rockfish}
Lines indicate the critical threshold for persistence as a function of harvesting rate on the y-axis and climate velocity as a fraction of the length of the viable patch on the x-axis from an approximated Gaussian dispersal kernel as parameterized for black rockfish. }
 \end{figure}

 \begin{figure}[h]
 \centering
 \includegraphics[width=.75\textwidth]{../../plots/rockfisheqbiomass.pdf}
 \caption{ \label{synergy_rockfish}
 (a) The equilibrium biomass of the population as a function of the climate velocity relative to patch length on the x-axis and the proportional harvesting rate on the y-axis. (b) Interaction between the two stressors as a function of climate velocity and harvesting rate. The heat map indicates the interaction measure $S$, i.e., the loss in biomass in the doubly stressed population in excess of the sum of the losses caused by each stressor individually ($E_{hc}-E_h-E_c$). $S$ of $0$ indicates additive interaction of the stressors. The excess loss, on the order of $0.001$, is small in comparison to the total biomass, which can be as large as $20$. These results are from an approximated Gaussian dispersal kernel as parameterized for  black rockfish.
 }
 \end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{../../plots/rockfish_sims.pdf}
\caption{\label{simulation_rockfish} The equilibrium biomass of the population as a function of the climate velocity relative to patch length on the x-axis and the harvesting rate on the y-axis under alternative management strategies as parameterized for black rockfish. (a) The equilibrium biomass for simulations with constant harvest rates. (b) Equilibrium biomass for simulations with threshold management. For threshold management, the maximum threshold below which no harvesting is allowed is set to be the largest population size observed at a given time step before harvesting. For a less sever threshold, we use a proportion of this maximum threshold, so that a lower proportion gives a lower threshold and allows for more harvesting. We show this proportion on the y-axis. (c) Equilibrium biomass for simulations with protected areas where harvesting pressure outside reserves unchanged. (d) Equilibrium biomass for simulations with protected areas with harvesting pressure reallocated outside reserves.}
\end{figure}

\cleardoublepage

\bibliography{fish}
